The Community Land Model, version 5.1 \\ One-at-a-time Parameter Perturbation Ensemble

### 2024-08-12 ms/ms.tex
refs

The second challenge involved defining a perturbation range for each parameter. We solicited expert judgment to set a minimum and maximum reasonable value for each parameter. In some cases, literature values were explicitly used (e.g. for the slope parameter of the stomatal conductance model, `medlynslope', \citeA{lin2015}), but the most common range was $\pm20\%$. It is exceedingly difficult to set parameter ranges that sample comparable probability density, even in a univariate experiment, like this one. The number of parameters is large, with many lacking sufficient empirical backing for robust range evaluation. Defining appropriate ranges for the full suite of land model parameters is a major activity of the scientific subdomains that comprise the land model (e.g. Kattge et al. 2020). Even with parameters that have an empirical basis, they may behave differently at the coarse climate modeling spatial resolution (zqz), complicating the process of uncertainty quantification. As such, we cannot claim that the parameters are equivalently sampled, whereby parameter effects and parameter rankings could be subject to sampling asymmetries.

>>>>

The second challenge involved defining a perturbation range for each parameter. We solicited expert judgment to set a minimum and maximum reasonable value for each parameter. In some cases, literature values were explicitly used (e.g. for the slope parameter of the stomatal conductance model, `medlynslope', \citeA{lin2015}), but the most common range was $\pm20\%$. It is exceedingly difficult to set parameter ranges that sample comparable probability density, even in a univariate experiment, like this one. The number of parameters is large, with many lacking sufficient empirical backing for robust range evaluation. Defining appropriate ranges for the full suite of land model parameters is a major activity of the scientific subdomains that comprise the land model \cite{kattge2020}. Even with parameters that have an empirical basis, they may behave differently at the coarse climate modeling spatial resolution (zqz), complicating the process of uncertainty quantification. As such, we cannot claim that the parameters are equivalently sampled, whereby parameter effects and parameter rankings could be subject to sampling asymmetries.
